%!TEX root = main.tex

\begin{thebibliography}{9}

  \bibook{ConcreteMath}{Ronald L. Graham, Donald E. Knuth and Oren Patashnik}{Concrete mathematics}{Addison-Wesley, Reading, MA, 1995.}
  \biburl{LogRegTutorial}{alias-i}{Logistic Regression Tutorial}{Lingpipe Home}{23 Nov. 2011}{http://alias-i.com/lingpipe/demos/tutorial/logistic-regression/read-me.html}
  \biburl{lid1}{Damir Cavar}{Language Identification LID Examples}{Personal Site}{9 Jan. 2012}{http://www.cavar.me/damir/LID}
  \biburl{lid2}{Arjen Poutsm}{Applying Monte Carlo Techniques to Language Identification}{Personal Site}{9 Jan. 2012}{http://ajwp.home.xs4all.nl/langident.pdf}
  \biburl{rapidminer}{Rapid-I}{Rapidminer}{Rapidminer site}{9 Nov. 2011}{http://rapid-i.com/content/view/181/190}
  \biburl{yahoo}{Yahoo! Directory}{Yahoo}{Yahoo}{10 oct. 2011}{http://dir.yahoo.com/}
  \biburl{tpanbtc}{Jason D. M. Rennie, Lawrence Shih, Jaime Teevan, David R. Karger}{Tackling the Poor Assumptions of Naive Bayes Text Classifiers}{MIT}{19 Jan. 2012}{http://people.csail.mit.edu/jrennie/papers/icml03-nb.pdf}
  \biburl{mmceo}{Dan Klein, Chris Manning}{Maxent Models, Conditional Estimation, and Optimization}{Stanford University}{19 Jan. 2012}{http://www.cs.berkeley.edu/~klein/papers/maxent-tutorial-slides.pdf}
  \biburl{epmem}{Joshua Goodman}{Exponential Priors for Maximum Entropy Models}{Microsoft}{19 Jan. 2012}{http://acl.ldc.upenn.edu/N/N04/N04-1039.pdf}
  \biburl{umetc}{Kamal Nigam, John Lafferty, Andrew McCallum}{Using Maximum Entropy for Text Classification}{Carnegie Mellon University}{19 Jan. 2012}{http://www.kamalnigam.com/papers/maxent-ijcaiws99.pdf}
  \biburl{tscdst}{Alec Go, Richa Bhayani, Lei Huang}{Twitter Sentiment Classification using Distant Supervision}{Stanford University}{19 Jan. 2012}{http://www.stanford.edu/$\sim$alecmgo/papers/TwitterDistantSupervision09.pdf}
  \biburl{ericsson}{Johan Wibergh}{Traffic and Market Data report}{Ericsson}{5 Apr. 2012}{http://hugin.info/1061/R/1561267/483187.pdf}
  \biburl{articles}{Henning Schulzrinne and co}{Writing Technical Articles}{Columbia University}{4 Apr. 2012}{http://www.cs.columbia.edu/~hgs/etc/writing-style.html}
  \biburl{flowsight}{Zhilabs}{About Flowsight}{Zhilabs}{10 Apr. 2012}{http://www.zhilabs.com/cms/?page\_id=643}
  \biburl{latex1}{Prof. (Dr.) K. S. S. Nambooripad}{On-line Tutorial on LaTex}{Indian TeX Users Group}{21 Feb. 2012}{http://www.tug.org/tutorials/tugindia/chap08-scr.pdf} 
\end{thebibliography}

